---
title: "Report of Kaggle Question Practice- Titanic"
author: "Li Cheng-En"
date: "7/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Motivation

As a student who stayed in the department of finance, statistic is important to me. Furthermore, the issue of big data was popular, it also highlight the importance of statistic. R is a good tool to

I also have written several codes of R. For more details about my codes, please see <https://github.com/Datoto1205/R-Practice>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
